A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-20 PPSN2016/paper.Rnw
Back to 10 pages

In fact, Table \ref{tab:correlation}, which shows
the correlation between the number of IPs from one minute to the
next, presents a similar  behavior for all experiments but the last one: a
very high correlation indicating that the number of volunteers changes
slowly. The {\tt cachereboot} experiment correlation indicates a bigger
dynamism, with individuals joining and leaving the experiment all the
time. This might be circumstantial, but it also informs the fact
that the solution is found in less time and that users need less
contributions to find it.

>>>>

In fact, Table \ref{tab:correlation}, which shows
the correlation between the number of IPs from one minute to the
next, presents a similar  behavior for all experiments but the last one. A high correlation indicating that the number of volunteers changes
slowly from one minute to the next; however, the {\tt cachereboot} experiment correlation indicates a bigger
dynamism, with volunteers joining and leaving the experiment all the
time, maybe because experiments take less time and need less resources.
